### 2021-03-31 written/eLifeRevision/Bittner_eLife2020.tex
more sc updates

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/fig3/fig3.pdf}
\end{center}
\caption{\footnotesize 
\textbf{A}. Rapid task switching behavioral paradigm (see text). 
\textbf{B}. Model of superior colliculus (SC). Neurons: LP - left pro, RP - right pro, LA - left anti, RA - right anti. 
Parameters: $sW$ - self, $hW$ - horizontal, $vW$ -vertical, $dW$ - diagonal weights.  
\textbf{C}. The EPI inferred distribution of rapid task switching networks.  
Red and purple stars ($\mathbf{z}_1$ and $\mathbf{z}_2$) indicate different connectivity regimes with different sensitivity vectors $\mathbf{v}_1$ and $\mathbf{v}_2$.
(Middle-left) EPI predictive distribution of task accuracies.
(Bottom-left) Task accuracy along dimensions of sensitivity in each connectivity regime.
\textbf{D}. Means (solid) and standard deviations (shaded) of each population across random simulated trials.
Top plots show Pro (top) and Anti (bottom) responses for connectivity $\mathbf{z}_1$.
Bottom rows show the same $\mathbf{z}_2$.
\textbf{E}. The EPI distribution predicts experimental results (left) showing no change in the Pro task, but larger error in the Anti task (right).
\textbf{F}. Accuracy in the Anti task during delay period optogenetic inactivation $p_{A,\text{opto}}$ is strongly anticorrelated with accuracy in the Pro task.
\textbf{G}. Accuracy with delay period inactivation along each connectivity regime's dimension of sensitivity.
}
\label{fig:SC}
\end{figure}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC2/figSC2.pdf}
\end{center}
\caption{\small (SC2):  
\textbf{A}. Simulations in network regime $\mathbf{z}_1$ (center) with simulations given connectivity perturbations in the negative direction of the sensitivity vector $\mathbf{v}_1$ (left) and positive direction (right).
\textbf{B}. Same as A for network regime $\mathbf{z}_2$.
}
\label{fig:SC2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.9]{figures/figSC3/figSC3.pdf}
\end{center}
\caption{\small (SC3):  
\textbf{A}. Invariant eigenvectors of connectivity matrix $W$.
\textbf{B}. Eigenvalues of connectivities of EPI distribution versus task accuracies.
}
\label{fig:SC3}
\end{figure}

@@

\begin{figure}
%\begin{center}
%\includegraphics[scale=0.8]{figures/figSC4/figSC4.pdf}
%\end{center}
\caption{\small (SC4):  \textbf{A}. Something showing differences in regimes.
}
\label{fig:SC4}
\end{figure}

@@

Writing the EPI distribution as a maximum entropy distribution, $T(\mathbf{x}, \mathbf{z})$ is comprised of both these first and second moments of the accuracy in each task (as in Equations \ref{eq:moments} and \ref{eq:mu_opt})
\begin{equation} 
T(\mathbf{x}; \mathbf{z}) = \begin{bmatrix} p_P(\mathbf{x}; \mathbf{z}) \\ p_A(\mathbf{x}; \mathbf{z}) \\ \left(p_P(\mathbf{x}; \mathbf{z}) - 75\% \right)^2 \\ \left(p_A(\mathbf{x}; \mathbf{z}) - 75\% \right)^2 \end{bmatrix},
\end{equation}
\begin{equation} 
\bm{\mu}_{\text{opt}} = \begin{bmatrix} 75\% \\ 75\% \\ 7.5\%^2 \\ 7.5\%^2 \end{bmatrix}.
\end{equation}
Throughout optimization, the augmented Lagrangian parameters $\eta$ and $c$, were updated after each epoch of 2,000 iterations(see Section \ref{methods_AL_opt}).  
The optimization converged after six epochs (Fig. \ref{fig:SC5}).

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{figures/figSC6/figSC6.pdf}
\end{center}
\caption{\small (SC6): 
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 20,000 iterations following the tenth augmented Lagrangian epoch.
}
\label{fig:SC5}
\end{figure}

For EPI in Fig. \ref{fig:SC}C, we used a real NVP architecture with three coupling layers of affine transformations parameterized by two-layer neural networks of 50 units per layer.
The initial distribution was a standard isotropic gaussian $z_0 \sim \mathcal{N}(\mathbf{0}, I)$ mapped to a support of $\mathbf{z}_i \in [-5, 5]$. 
We used an augmented Lagrangian coefficient of $c_0 = 10^{2}$, a batch size $n=100$, and $\beta=2$.
The distribution shown is that of the architecture converging with criteria $N_{\text{test}} = 25$ at greatest entropy across random seeds.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/fig3/fig3.pdf}
\end{center}
\caption{\footnotesize 
\textbf{A}. Rapid task switching behavioral paradigm (see text). 
\textbf{B}. Model of superior colliculus (SC). Neurons: LP - left pro, RP - right pro, LA - left anti, RA - right anti. 
Parameters: $sW$ - self, $hW$ - horizontal, $vW$ -vertical, $dW$ - diagonal weights.  
\textbf{C}. The EPI inferred distribution of rapid task switching networks.  
Red and purple stars indicate modes $\mathbf{z}^*$ of each connectivity regime.
Sensitivity vectors $\mathbf{v}_1(\mathbf{z}^*)$ are shown by arrows.
(Bottom-left) EPI predictive distribution of task accuracies.
\textbf{D}. The connectivity regimes have different responses to perturbation.
(Top) Mean and standard error ($N_{\text{test}}$ = 25) of accuracy with respect to perturbation along the sensitivity dimension of each mode $\mathbf{z}^*$.
(Middle) Same with perturbation in the dimension of increasing $\lambda_{\text{task}}$ ($\mathbf{v}_{\text{task}}$).
(Bottom) Same with perturbation in the dimension of increasing $\lambda_{\text{diag}}$ ($\mathbf{v}_{\text{diag}}$).
}
\label{fig:SC}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/fig5/fig5.pdf}
\end{center}
\caption{\footnotesize 
\textbf{A}. The EPI distribution predicts experimental results (left) showing no change in the Pro task, but larger error in the Anti task (right).
\textbf{B}. Accuracy in the Anti task during delay period optogenetic inactivation $p_{A,\text{opto}}$ is strongly anticorrelated with accuracy in the Pro task.
\textbf{C}. Mean and standard error ($N_{\text{test}}$ = 25) of accuracy with respect to perturbation along the sensitivity dimension of each mode $\mathbf{z}^*$.
}
\label{fig:SC_opt}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.7]{figures/figSC2/figSC2.pdf}
\end{center}
\caption{\small (SC2):  
\textbf{A}. Simulations in network regime 1 ($hW_{\text{fixed}} = -1.2$) (center) with simulations given connectivity perturbations in the negative direction of the sensitivity vector $\mathbf{v}_1$ (left) and positive direction (right).
\textbf{B}. Same as A for network regime 2.
}
\label{fig:SC2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.9]{figures/figSC3/figSC3.pdf}
\end{center}
\caption{\small (SC3):  
\textbf{A}. Invariant eigenvectors of connectivity matrix $W$.
\textbf{B}. Accuracies for connectivity perturbations for increasing $\lambda_{\text{all}}$ and $\lambda_{\text{side}}$ (rest shown in Fig. \ref{fig:SC}D).
}
\label{fig:SC3}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC4/figSC4.pdf}
\end{center}
\caption{\small (SC4):  \textbf{A}. Shows how eigvals change throughout blah
}
\label{fig:SC4}
\end{figure}

@@

Writing the EPI distribution as a maximum entropy distribution, $T(\mathbf{x}, \mathbf{z})$ is comprised of both these first and second moments of the accuracy in each task (as in Equations \ref{eq:moments} and \ref{eq:mu_opt})
\begin{equation} 
T(\mathbf{x}; \mathbf{z}) = \begin{bmatrix} p_P(\mathbf{x}; \mathbf{z}) \\ p_A(\mathbf{x}; \mathbf{z}) \\ \left(p_P(\mathbf{x}; \mathbf{z}) - 75\% \right)^2 \\ \left(p_A(\mathbf{x}; \mathbf{z}) - 75\% \right)^2 \end{bmatrix},
\end{equation}
\begin{equation} 
\bm{\mu}_{\text{opt}} = \begin{bmatrix} 75\% \\ 75\% \\ 7.5\%^2 \\ 7.5\%^2 \end{bmatrix}.
\end{equation}
Throughout optimization, the augmented Lagrangian parameters $\eta$ and $c$, were updated after each epoch of 2,000 iterations (see Section \ref{methods_AL_opt}).  
The optimization converged after ten epochs (Fig. \ref{fig:SC6}).

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{figures/figSC6/figSC6.pdf}
\end{center}
\caption{\small (SC6): 
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 20,000 iterations following the tenth augmented Lagrangian epoch.
}
\label{fig:SC6}
\end{figure}

For EPI in Fig. \ref{fig:SC}C, we used a real NVP architecture with three coupling layers of affine transformations parameterized by two-layer neural networks of 50 units per layer.
The initial distribution was a standard isotropic gaussian $z_0 \sim \mathcal{N}(\mathbf{0}, I)$ mapped to a support of $\mathbf{z}_i \in [-5, 5]$. 
We used an augmented Lagrangian coefficient of $c_0 = 10^{2}$, a batch size $n=100$, and $\beta=2$.
The distribution converged with criteria $N_{\text{test}} = 25$.
